%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\linespread{1.3}
%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape James Thomas} \\ \vspace{1pt}
    \small 07748241847 $|$ \href{mailto:x@xcom}{\underline{eidolon123.com}} $|$ 
    \href{https://linkedin.com/in/x}{\underline{linkedin.com/in/jamesthomas1999}} $|$
    \href{https://github.com/x}{\underline{github.com/Eidolon123}}
\end{center}

%-----------Intro-----------
\hfill \break
Current third year at Coventry University studying Ethical Hacking and Cyber Security looking to secure a graduate position in a penetration testing role.
Highly ambitious and motivated in areas surrounding penetration testing, reverse engineering, code development/analysis and general problem solving. Experienced in leadership roles and high-pressure situations.

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Coventry University}{2019-2022}
      {Bachelor of Science - Ethical Hacking and Cyber Security}{Expected graduation - 2022}
          \resumeItemListStart
            \resumeItem{\textbf{First Year} - 1st}\\ 
            - The initial year of university allowed me to gain experience working in a team on more technical projects. In these situations, I would always take on a leadership role within the team.
            My proficiency in the programming languages Python, C and C++ was also improved throughout the year. Outside of my studies, I worked on improving my social skills by attending the COMSEC society as well as meeting new people outside of the course.
            \resumeItem{\textbf{Second Year} - 1st}\\
            - My technical knowledge of cryptography standards, operating systems and penetration testing was worked on during this year. 
            I also had the opportunity to work on a group based 'real world project' utilising the sprint method of agile development. In this group, I again took on a leadership role.
            I focused as well on the ethical, legal and social issues surrounding penetration testing and hacking in general, providing me with a working knowledge of the laws that govern the profession.
            \resumeItem{\textbf{Third Year} - Expected 1st}\\
            - Developed skills in code analysis, exploit development, SOC management and advanced network design.
            Further developed skills in pentesting situations against both windows and Linux targets.
            My dissertation constitutes developing a containerised honeypot of simulated IOT devices deployed in a Kubernetes cluster on the Azure platform, in order to analyse threat methodology against IOT technology.
            This project has allowed me to learn new skills in Kubernetes and container management and cloud computing.
            \resumeItem{\textbf{Extra Modules} - CISCO Networking, Project Management, Academic Writing}
        \resumeItemListEnd
    \resumeSubheading
      {Penwith College}{2016-2019}
      {A-Levels and Subdiploma}{}
          \resumeItemListStart
            \resumeItem{Maths A-Level - B}
            \resumeItem{Physics A-Level - C}
            \resumeItem{Comp Sci A-Level - C}
            \resumeItem{IT Subdiploma - D*}
          \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Previous Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {General Assistant}{2016 – 2018}
      {J R Sainsbury's}{}
      \resumeItemListStart
        \resumeItem{While working to save money for university I was required to work in a team consisting of different colleagues each shift. Often tight time limits were placed on the work resulting in a dynamic, high-pressure work environment. My customer facing skills were also developed during this time as each customer's request had to be met with high levels of professionalism. I left this job to focus on my education.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

    \newpage
%-----------PROJECTS-----------
\section{Projects and Hobbies}

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Linux Ricing} $|$ \emph{Scripting, System and Network Management}}{2018 -- Present}
          \resumeItemListStart
            \resumeItem{Customising Linux distributions}\\
            - Through customising and daily driving Arch Linux (btw) I have developed a thorough working knowledge of Linux system maintenance.
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{CTF competitions} $|$ \emph{Team - R0073R5}}{2019 - Present}
          \resumeItemListStart
            \resumeItem{SPBCTF - 56th/246}
            \resumeItem{Nettitude Uni Challenge - 1st}
            \resumeItem{pwnED - 9th/50}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Rugby} $|$ \emph{Team building, Physical development, Decision making}}{2005 -- 2020}\\
          \hfill \break
          I achieved the role of captain/vice-captain/squad captain while playing for the Cornish Pirates, developing my leadership, communication and decision making skills. By performing at a high level I was selected for the county team for multiple years allowing me to experience higher pressure situations with tougher requirements. By performing well under the higher pressure I was then selected for the Exeter Chief development squad where I participated in a tournament with all of the premiership team development squads. I stopped playing under medical advice after multiple injuries.
          \resumeProjectHeading
          {\textbf{General Hobbies}  \emph{}}{}\\
          \hfill \break
          When I'm not working I enjoy reading science fiction and fantasy books, listening to podcasts about self-development and comedy and caring for my collection of plants.
    \resumeSubHeadingListEnd

\end{document}
